---
title: "Aids Drug"
author: "Giulianni P"
date: "Fall 2022"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
Females=filter(triUmp,gender== "F")  
DrugUsers=filter(triUmp,DrugUser== "yes")
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aids drug (triUmpsal) is under test in clinical trials. Consider the DrugUsers, does this drug seem effective on this group?  Hint - use dplyr to obtain that sub-population with the filter command.  Next, repeat the analysis on just females, does this drug seem effective on women?

<!-- Be sure to produce Descriptive Results and Inferential Results for both groups. !-->

# Methods

The questions are 1. Is the vaccine is effective for Drug users?, 2. Is the vaccine effective for women?.  

$H_0$: The vaccine is not effective for Drug users. 
$HA_0$: The vaccine is effective for Drug users.  

$H_0$: The vaccine is not effective for women.  
$HA_0$: The vaccine is effective for women.  

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed, for example sub-setting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~infected + treatment,data=DrugUsers)
barchartGC(~infected + treatment,data=DrugUsers, type="percent")

```

Based on the graph above, we can determine that those with the vaccine overall had a better reaction to those than aids.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe patterns, if any, that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming to or departing from what is expected by the null hypothesis !-->

### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=DrugUsers)
rowPerc(table1)
colPerc(table1)
```
Among all those who were infected, DrugUsers showed about 25% got the vaccine but 75% had the Placebo,this suggests that the vaccine is effective on DrugUsers.


<!--Numerical results go here. Use the numerical results to describe the patterns, if any, that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
table1 <- xtabs(~infected + treatment, data=DrugUsers)
rowPerc(table1)
colPerc(table1)
```
Based on the P-Value being less than .005 tells us that we can reject the null hypothesis, Determining that The vaccine was significant to DrugUsers. 

```{r}
barchartGC(~infected + treatment,data=Females)
barchartGC(~infected + treatment,data=Females, type="percent")

```

The chart shown above suggests that women using vaccines are more likely to get aids.


### Numerical Summaries  

```{r}
table1 <- xtabs(~infected + treatment, data=Females)
rowPerc(table1)
colPerc(table1)
```
This Numerical summary shows that the likelihood of getting aids for females is high even with the vaccine

## Inferential  
```{r}
table1 <- xtabs(~infected + treatment, data=Females)
rowPerc(table1)
colPerc(table1)
```

From the P-value that we've recieved we can reject the null hypothesis due to it being less than .005

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->
  
# Discussion and Conclusion

 Is the vaccine is effective for Drug users?
 Based on the Information given Those who were Drug users are still likely to get aids.

 Is the vaccine effective for women?.
 There was a significance in women but not a good one as the vaccine made women more susceptible to contracting aids.


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the George Town videos collection.!

Report on both Drug Users and Females.  Be sure to include the odds for both groups.
-->

 
